Predicting sales of newly published books

### 2015-08-13 paper.tex
Revised introduction

% A una empresa, lanzar un nuevo producto le supone un alto riesgo debido a la complejidad de los procesos de producción y distribución. En este ámbito, disponer de estimaciones de futuras ventas del nuevo producto resulta extremadamente importante \cite{ChingChin2010}.
A company that intends launching a new product has a high risk due to the complexity of the production and distribution processes. 
A newly launched product is also new to the company, and sales forecasts can be based on the experience of similar products.
In this scope, having accurate estimates of future sales of the new product is extremely important \cite{ChingChin2010}.

% La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
In this sense, the publishing industry is based on very particular and established production processes, and publishing a book requires several steps, between whom the distribution is important and plays an important role.
% Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
The publishing process and individual decisions at each step are very important. One of those decisions is the number of copies to print.

% Así pues, un sistema de predicción debe tener en cuenta muchos detalles acerca del funcionamiento del proceso editorial.
Thus, a suitable prediction system for new book publishing should take into account many details about how the editorial process works.

% La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
Implementing a good forecasting tool requires not only a good study of the state of the art in this field, but also an accurate knowledge of the operations and challenges facing the publishing industry and its supply chain.

% En el ámbito de la industria de la moda se trata de un problema muy complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se ha abordado con diversos métodos en las últimas décadas \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.
In the field of fashion industry it is very complex problem, subject to certain requirements \cite{SThomassey2014} and has been faced using various methods in recent decades \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.

% Interesa imprimir un número de ejemplares suficiente pero sin pasarse, ya que los no vendidos suponen pérdidas, mientras que si se imprimieron de menos, siempre se pueden imprimir más.
In the field of publishing industry, it is more important printing an adequate number of copies but not too much, as the unsold volumes will lead to losses, whereas if the number of printed copies was not enough, you can always print more. Thus, it is extremely important to forecast the sales a new book might achieve.

% El uso de una herramienta de predicción es útil si se usa adecuadamente, y para ello conviene conocer el producto, las características de las ventas y la forma de distribuirlo, ya que son detalles que afectan al proceso \cite{Armstrong2001,SThomassey2014}.
Thus, using a predictive tool is very useful when used properly; in this sense, it is very important to know the product, the characteristics of sales and how to distribute it, as those details affect the process \cite{Armstrong2001,SThomassey2014}.

% En la industria editorial influyen diversos factores que hacen que las ventas fluctúen. Estos factores no suelen ser controlables y en ocasiones no son conocidos. Algunos tienen que ver con las decisiones sobre compras, otros con el tráfico de mercancías o con la estrategia de distribución \cite{Little1998}.
The publishing industry is influenced by various factors that make sales fluctuate. 
These factors are usually not controllable and even, sometimes are not known.
Some have to do with decisions on purchases, others with freight traffic, and others with the distribution strategy \cite{Little1998}.

@@

% En la bibliografía se pueden encontrar diversas propuestas para llevar a cabo la predicción de ventas en diferentes áreas. Por un lado, ciertos métodos cualitativos se basan en la experiencia de expertos, mientras que los métodos basados en el análisis de series temporales utilizan información histórica para hacer las predicciones \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
In the literature several proposals to perform the prediction of sales in different areas can be found. 
On the one hand, several qualitative methods are based on an expert experience, while time series prediction methods are based on using historical data to make predictions \cite{ChingChin2010,FaderHardie2005,Madsen2008}.

@@

Sales forecasting in editorial industry is a very complex problem.
There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.

@@

Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka\footnote{{\tt http://www.cs.waikato.ac.nz/ml/weka/}} tool \cite{Hall2009,Witten2011} have been choosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using these methods.

@@

%********************************************************************************
\section*{Acknowledgements}
This work has been supported in part by SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity), SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17 GENIL project (CEI-BIOTIC Granada).

>>>>

% A una empresa, lanzar un nuevo producto le supone un alto riesgo debido a la complejidad de los procesos de producción y distribución. En este ámbito, disponer de estimaciones de futuras ventas del nuevo producto resulta extremadamente importante \cite{ChingChin2010}.
A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. A newly
launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales.

% La industria editorial se basa en varios pasos y procesos productivos / La publicación de un libro requiere de varios pasos / Además, la distribución es importante y juega un papel importante
In this sense, the publishing industry is based on very particular and
established production process, and publishing a book requires several
steps, between which the distribution is important and plays an
important role. 
% Esos pasos hacen que el proceso y las decisiones individuales en cada paso sean muy importantes. Una de esas decisiones es el número de ejemplares a imprimir.
The publishing process and individual decisions at each step are very
important. One of those decisions is the number of copies to print. % ¿Esto que tiene que ver con la frase anterior? - JJ

% Así pues, un sistema de predicción debe tener en cuenta muchos detalles acerca del funcionamiento del proceso editorial.
Thus, a suitable prediction system for new books should take into
account many details about how the editorial process works. % y? - JJ

% La implementación de un buen sistema de predicción requiere, no sólo de un buen estudio del estado del arte en este campo, sino también de un conocimiento preciso de las operaciones y retos de la industria editorial y su cadena de producción.
Implementing a good forecasting tool requires not only a good study of
the state of the art in this field, but also an accurate knowledge of
the operations and challenges facing the publishing industry and its
supply chain. % ¿eso es lo que vamos a hacer? - JJ

% En el ámbito de la industria de la moda se trata de un problema muy
% complejo, sujeto a ciertos requisitos \cite{SThomassey2014} y que se
% ha abordado con diversos métodos en las últimas décadas
% \cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}. 
% Pero ¿a santo de qué viene aquí la industria de la moda? Habrá que
% introducirlo diciendo... El problema de la industria similar es
% parecido a otras industrias, etc, etc...

In the field of fashion predicting sales is very complex problem, subject
to certain requirements \cite{SThomassey2014} and has been faced using
various methods in recent decades
\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.  % Este
                                % párrafo no dice absolutamente nada
                                % ni aporta nada. Si se menciona la
                                % industria de la moda, es que vamos a
                                % aprender algo de ella. ¿Cuáles son
                                % los requisitos? ¿Cuáles son los
                                % métodos? ¿Vamos a aprender de ellos?
                                % - JJ

% Interesa imprimir un número de ejemplares suficiente pero sin pasarse, ya que los no vendidos suponen pérdidas, mientras que si se imprimieron de menos, siempre se pueden imprimir más.
In the field of publishing industry, it is more important printing an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. Thus, it is extremely important to
forecast the sales a new book might achieve. % Hala, otro salto. ¿Qué
                                % tiene que ver esto con el párrafo
                                % anterior? - JJ

% El uso de una herramienta de predicción es útil si se usa adecuadamente, y para ello conviene conocer el producto, las características de las ventas y la forma de distribuirlo, ya que son detalles que afectan al proceso \cite{Armstrong2001,SThomassey2014}.
Thus, using a predictive tool is very useful when used properly; in
this sense, it is very important to know the product, the
characteristics of sales and how to distribute it, as those details
affect the process \cite{Armstrong2001,SThomassey2014}. % ¿Esto
                                % también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ

% En la industria editorial influyen diversos factores que hacen que las ventas fluctúen. Estos factores no suelen ser controlables y en ocasiones no son conocidos. Algunos tienen que ver con las decisiones sobre compras, otros con el tráfico de mercancías o con la estrategia de distribución \cite{Little1998}.
Book sales are influenced by various factors that make
them fluctuate.  These factors are usually not controllable and
sometimes unknown. 
Some have to do with decisions on purchases, others with freight
traffic, and others with the distribution strategy
\cite{Little1998}. % ¿Qué hacen todas estas cosas? ¿Vamos a tenerlas
                   % en cuenta?

@@

% En la bibliografía se pueden encontrar diversas propuestas para llevar a cabo la predicción de ventas en diferentes áreas. Por un lado, ciertos métodos cualitativos se basan en la experiencia de expertos, mientras que los métodos basados en el análisis de series temporales utilizan información histórica para hacer las predicciones \cite{ChingChin2010,FaderHardie2005,Madsen2008}.
In the literature several proposals to perform the prediction of sales in different areas can be found. 
On the one hand, several qualitative methods are based on an expert
experience, while time series prediction methods are based on using
historical data to make predictions
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
                                % dicho cuál es el problema. Tienes
                                % que decir claramente qué tienes y
                                % qué quieres. - JJ

@@

Sales forecasting in editorial industry is a very complex
problem. %hala, vuelta la burra al trigo - JJ
There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.

@@

Thus, in this research five forecasting methods, based on the literature review in the introduction \cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool
\cite{Hall2009,Witten2011} have been choosen, as these methods are
widely known, and could be very helpful for practitioners to reproduce
experiments and even to solve similar sales prediction problems using
these methods. % eliminado el pie de página, es mejor usar referencias
               % - JJ

@@

%********************************************************************************
\section*{Acknowledgements}
This work has been supported in part by SIPESCA (Programa Operativo
FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14
(Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17
GENIL project (CEI-BIOTIC Granada). % ¿Y el contrato con Trevenque?  - JJ
